\documentclass{article}
\usepackage[utf8]{inputenc}

\linespread{2}

\usepackage[margin=0.5in]{geometry}

\title{D03 Gender and Computing}
\author{William Mak}
\date{November 2014}

\begin{document}

\maketitle

I first got into computing around the age of 11, my friend and I wanted to make
a game after playing Age of Empires together. After going through the tutorial
for creating something basic in Visual Basic I found it too difficult and gave
up until I was in high school. At that point I took an Informational Technology
course which taught me how to use programs like Microsoft Office and Powerpoint.
Which I was sorely disappointed with. After that I took Computer Engineering and
Computer Science which introduced me to things like turing, pascal, circuits. My
father is in computer science so he encouraged my interest and my mother liked
that I did better in these classes so she also encouraged my interest in
computing. I don't think I would've have acted differently if I was a female, if
anything I noticed that the females in my class did better. 

I feel like the only advantage I have would be the stigma associated with
females in computer science. I've talked to people who refer to attractive
females in computer science as unicorns. The fact that they're so very rare
would probably ward away the majority of females who don't want this image
associated with them. But I've noticed this in the reverse, at my previous place
of employment I recall my boss mentioning that he wanted to give a candidate an
interview specifically because they were female and that our team didn't have
any females.

Yes I intend to stay in computer science as my career. As of right now I'm
already applying for various positions. No I do not expect my gender to
influence my prospects, even with my earlier mention of my boss wanting to give
a candidate an interview he said so jokingly and still used the capabilities of
each candidate to make his decision. In my biased opinion companies are
generally more concerned with how skilled someone is and not their gender

Yes computers still seem to be a male thing in my opinion. Which is not to say I
think this should be how they should seem. Just given my experiences in life
this is what I think. The majority of people I know in Computer Science are
male. There are only four females of whom I play video games with on a regular
basis compared to the number of males this is a very small number. I also think
that most women think about computers differently than I do. I find that most of
them think of their computers as a tool for things like word processing and
browsing the web. While I think that a computer is a tool to do difficult
things. A computer can sort a list of a billion items in the blink of an eye for
example but most people just see it as something to share pictures with. I think
I'm a nerd, I spend most of my day on my computer. I find it a point of pride
that my operating system is a linux distribution. I have spent hours customizing
various configuration files to get my computer exactly how I want it. I'm using
\latex to type this paper up because I think it's the best way to write a
document. And when I compare this to my friends who I don't think as nerds they
would never do any of that.

Yes women who are interested in computing probably have different interests than
those who are not. Much like it is with men. I generally find that people
interested in computing are more into the "nerd" culture liking things like
gaming and technology. So I think that this would be the same for both men and
women.

\end{document}
